### 2019-01-12 tex/manuscript.tex
revised microstructure

%650 words here

@@

	MIGHT BE GOOD TO SIGNPOST HERE... we discuss each of these lines of evidence in the sections below beginning with a consideration of the impact of microstructure, then we talk about mechanical testing, blah blah. Emphasize that this is key to predicting and understanding the mechanical behavior of the snout during bending.
%stick to 600 words for each results section and 500 words for conclusions
	\section{Microstructure of the rostrum}\label{sec:microstructure} %750 words here (1400 total)
		The cuticle of arthropods, including insects, is made up of chitin and numerous uncharacterized proteins, which effectively act as a matrix into which the chitin is embedded \cite{Nikolov2011,Nikolov2010,Vincent2004}.
		The cuticle is strongly influenced by its chemical properties, especially the degree of tanning and overall water content, but the arrangement of the embedded chitin fibers is primarily responsible for the its unique mechanical behavior \cite{Klocke2011,Vincent2004}.	
		Accordingly, the cuticle is often considered as a fiber-reinforced composite material; however, in beetles, the composite arrangement of the chitin fibers varies by cuticle region.

		The insect cuticle can generally be divided into three regions (Figs.~INSERT-REFS-HERE), including (1) endocuticle, which is the most compliant and innermost region; and (3) exocuticle, which is the outermost region, usually the stiffest and hardest, and coated by a waxy secretion (epicuticle) that is not of great mechanical significance in most groups.
		Between these regions lies (2) the mesocuticle, which is similar in microstructure to exocuticle, but exhibits a lesser degree of tanning (sclerotization) and usually serves as a transition zone to the endocuticle \cite{Klocke2011,Vincent1982,Vincent2004}.

		In general, these regions are confluent, and not necessarily sharply defined; for instance, the mesocuticle is not always evident, and is sometimes considered part of the exocuticle.
		In beetles, both the exocuticle and mesocuticle (when present) are laminate, and have numerous laminae of unidirectional chitin fibers, one layer thick (2-4nm each), embedded in a proteinaceous matrix.
		These layers are stacked at a more or less constant angle to each other in a helicoidal arrangement, referred to as the Bouligand structure \cite{Blackwell1980,Bouligand1972,Neville1976}. 
		This microstructural arrangement allows the cuticle to exhibit transverse isotropy, or complete isotropy in some cases, despite the strong anisotropy of $\alpha$-chitin.

		Conversely, the endocuticle of Coleoptera appears to take advantage of this anisotropy to improve fracture resistance of the exoskeleton.
		Beetles in particular have a highly modified endocuticle made up of large (5-20$\mu$m OD) unidirectional bundles of chitin, called ``balken'' (German for beam, strut) or macrofibers; these macrofibers are aligned in layers, as in Figs~INSERT-FIGS-HERE \cite{Kamp2010,Kamp2015}.
		Typically, the endocuticle contains several layers of macrofibers, in which adjacent layers form pairs. 
		The layers within each pair are pseudo-orthogonal (i.e., angled approx. $90\degree$ to each other, see Figs.~INSERT-REFS-HERE), while the stacking angle between pairs is typically much shallower, although some other configurations have been observed \cite{Hepburn1973,Kamp2010}.
		It is thought that this arrangement of the macrofibers contributes to the high toughness of beetle exoskeletons by inhibiting crack formation and propagation between successive layers \cite{Kamp2010,Kamp2015,Hepburn1973}.

		We have found that in \textit{Curculio}, the head capsule (as in the rest of the body) exhibits this general arrangement of the endocuticle, with an angle of approximately $30\degree$ between successive pseudo-orthogonal plies.
		Additionally, the head capsule has roughly equal thicknesses of exocuticle and endocuticle along its surface in cross section; qualitatively, manipulating this part of the head with forceps quickly reveals that this part of the head is quite rigid.

		By contrast, the region beyond the scrobe (antennal channel) is quite flexible, even in fully desiccated specimens.
		Serial thin sectioning of the snout has demonstrated that the cuticle in this region has substantially different composite properties in two key traits (see Fig~INSERT-REFS-HERE):

		\begin{enumerate}
			\item The exocuticle is reduced to a thin shell, with the endocuticle thickened to offset this reduction.
			\item The endocuticular macrofibers exhibit no rotation between successive pseudo-orthogonal plies, which are all oriented at approx. $45\degree$ to the longitudinal axis of the snout.
		\end{enumerate}

		In previous work we identified these modifications to the composite arrangement of the cuticle, but only within the species \textit{C. longinasus} Chittenden, 1927 \cite{Jansen2016, Singh2016}.
		These same modifications to the cuticle of the rostral apex have now been uncovered in a further six phylogenetically disparate species, listed below, thus indicating that this is likely a genus-wide phenomenon.

		Notably, we could find no evidence of resilin, as indicated by florescent microscopy, anywhere in the cuticle of the head (including the rostrum).
		We also observed no difference in the total thickness of the cuticle between the head capsule and rostral apex, only differences in relative layer thicknesses.
		In the next section, we demonstrate that that the endocuticle does not vary in tensile strength across the head, making it unlikely that there are significant differences in sclerotization or chitin composition within the exocuticle and endocuticle that might result in a more compliant cuticle.
		We therefor hypothesize that these differences in the microstructure of the cuticle in different regions of the head are solely responsible for the observed flexibility of the snout.

	\section{Tensile testing and fracture mechanics} %shoot for 550 words
		The predicted behavior of the snout is borne out by the data, where UTS is strongly correlated with the cross-sectional area of the endocuticle across species.

	\section{Fatigue testing of \textit{Curculio caryae}} %shot for 550 words

>>>>

%~650 words here

@@

	MIGHT BE GOOD TO SIGNPOST HERE... we discuss each of these lines of evidence in the sections below beginning with a consideration of the impact of microstructure, then we talk about mechanical testing, blah blah. Emphasize that this is key to predicting and understanding the mechanical behavior of the snout during bending.

%stick to 600 words for each results section and 500 words for conclusions
	\section{Microstructure of the rostrum}\label{sec:microstructure}
	%~700 words here (1500 total, shorten later)
		Insect cuticle is made up of chitin and numerous uncharacterized proteins, which effectively act as a matrix into which the chitin is embedded \cite{Nikolov2011,Nikolov2010,Vincent2004}.
		The arrangement of the embedded chitin fibers is primarily responsible for the mechanical behavior of the cuticle, although this is modulated by the degree of tanning and water retention. \cite{Klocke2011,Vincent2004}.	
		Accordingly, cuticle is often considered as a fiber-reinforced composite material; however, in beetles, the composite arrangement of the chitin fibers varies by cuticle region.

		Insect cuticle is divisible into three regions (Figs.~INSERT-REFS-HERE), including (1) endocuticle, which is the most compliant and innermost region; and (3) exocuticle, which is the stiffest, hardest, and outermost region.
		Between these lies (2) mesocuticle, which is similar in microstructure to exocuticle, but less sclerotized (tanned), usually acting as a thin transition zone \cite{Klocke2011,Vincent1982,Vincent2004}.

		In general, these regions are confluent, and not necessarily sharply defined; for instance, mesocuticle is not always evident, and is sometimes considered part of the exocuticle.
		In beetles, both exocuticle and mesocuticle (when present) are laminate, and have numerous laminae of unidirectional chitin fibers, each layer a single fiber thick (2-4nm), embedded in a proteinaceous matrix.
		These layers are stacked at a more or less constant angle to each other in a helicoidal arrangement, referred to as the Bouligand structure \cite{Blackwell1980,Bouligand1972,Neville1976}. 
		This microstructure allows exocuticle and mesocuticle to exhibit transverse isotropy, or complete isotropy in some cases, despite the strong anisotropy of $\alpha$-chitin.

		Conversely, the endocuticle of Coleoptera appears to take advantage of this anisotropy to improve fracture resistance of the exoskeleton.
		Beetles in particular have a highly modified endocuticle comprised of large (5-20$\mu$m OD) unidirectional bundles of chitin, called macrofibers.
		Macrofibers are aligned in layers, as in Figs~INSERT-FIGS-HERE \cite{Kamp2010,Kamp2015}.
		Typically, endocuticle contains several layers of macrofibers, with the adjacent layers forming pairs. 
		The layers \emph{within} each pair are pseudo-orthogonal (i.e., angled approx. $90\degree$ to each other, see Figs.~INSERT-REFS-HERE), while the stacking angle \emph{between} pairs is typically acute, although other configurations have been observed \cite{Hepburn1973,Kamp2010}.
		It is thought that this arrangement of the macrofibers contributes to the toughness of beetle exoskeletons by inhibiting crack formation and propagation between successive plies \cite{Kamp2010,Kamp2015,Hepburn1973}.

		We have found that in \textit{Curculio}, the head capsule (which is similar to the rest of the body) fits the general profile of endocuticle, with an angle of approximately $30\degree$ between successive pseudo-orthogonal plies.
		Additionally, in the head capsule, the thickness of the exocuticle in cross section is nearly equal to that of the endocuticle; compared to the snout, this part of the head is fairly rigid.

		By contrast, the region beyond the scrobe (antennal channel) is quite flexible, even in fully desiccated specimens.
		Serial thin sectioning of the snout has demonstrated that the cuticle in this region has a different composite structure (see Fig~INSERT-REFS-HERE) than the head capsule, namely:

		\begin{enumerate}
			\item The exocuticle is reduced to a thin shell, with the endocuticle thickened to offset this reduction.
			\item The endocuticular macrofibers exhibit no rotation between successive pseudo-orthogonal plies, which are all oriented at approx. $\pm45\degree$ to the longitudinal axis of the snout.
		\end{enumerate}

		Correspondingly, the portion of the snout between the head capsule and apex of the scrobe exhibits a gradual transition in composite profile along an anterior-posterior gradient.		
		In previous work we identified these modifications to the composite structure of the cuticle, but only within a single species, \textit{C. longinasus} Chittenden, 1927 \cite{Jansen2016, Singh2016}.
		This composite profile has now been uncovered in the rostral apex of six additional, phylogenetically disparate, species (listed below), indicating that this is likely a genus-wide trait.

		Notably, we could find no evidence of resilin, as indicated by florescent microscopy, anywhere in the cuticle of the head (including the rostrum).
		We also observed no difference in total cuticle thickness between the head capsule and rostral apex, only differences in relative layer thicknesses.
		Below we demonstrate that that the endocuticle does not vary in tensile strength across the rostrum, making it unlikely that differences in sclerotization or chitin composition within the cuticle are responsible for the mechanical behavior of the rostrum.
		The available evidence therefore suggests that the relative flexibility of the snout is solely derived from the composite profile of its cuticle.

	\section{Tensile testing and fracture mechanics} %shoot for 600 words
		Based on our understanding of the microstructure of the cuticle, it is possible to make several predictions about the mechanical behavior of the snout.
		First, we can predict that the endocuticle will contribute more to the tensile strength of the rostrum than the exocuticle, because the endocuticle is organized in large bundles of aligned, anisotropic fibers.
		Second, the endocuticle will be less brittle than the exocuticle, therefore we should expect that fractures will initiate in the exocuticle.
		The predicted behavior of the snout is borne out by the data, where UTS is strongly correlated with the cross-sectional area of the endocuticle across species.
		In addition to making the cuticle flexible, this profile makes it less likely to break, suggesting a possible means by which the system evolved (negative selection of breakage, maybe say this in conclusions).

		Outline:
		Intro
			To better characterize the mechanical behavior of the snout as an integrated whole, we performed tensile testing on the heads of 6 species in the genus \textit{Curculio}, representing a mixture of closely and distantly related taxa.
		Tensile testing
			We observed that the maximum force sustained at the site of the break was strongly correlated with the cross-sectional area of the endocuticle, and not the exocuticle.
			Consequently, there was a negative correlation between utlimate tensile strenth of the specimen and the ratio of exocuticle to endocuticle cross-sectional area at the site of fracture, indicating that as the proportion of exocuticle increased, tensile strength decreased.
			 All of these associations were found to be statistically significant and independent of species membership, rostrum length, and location on the snout.

			This strongly suggests that there is very little variation in the gross elastic behavior of the cuticle across the genus, in agreement with our current understanding of cuticle mechanobiology.

	\section{Fatigue testing of \textit{Curculio caryae}} %shot for 600 words
